%% ============================================================
%% ABSTRACT - TEMPLATE DESCRIPTION
%% ============================================================
\addcontentsline{toc}{chapter}{Abstract}
\chapter*{Abstract} % TODO: refine the abstract to better reflect the content of the thesis
This thesis details the design, construction, and validation of a programmable, small-scale anthropomorphic manipulator. The system is engineered for a 500 mm reach and a 1 kg maximum payload, featuring a 5-axis kinematic structure with an automatically calibrating, interchangeable end-effector. The mechanical assembly utilizes a hybrid construction of custom 3D-printed components with reinforced brass inserts, precision-cut aluminum sheets, and V-slot profiles.

To ensure precision and safety, the manipulator employs five NEMA17 stepper motors integrated into a closed-loop control system via rotary encoders. A key technical contribution is the implementation of active collision detection with adjustable force thresholds, facilitating safe interaction between the robot and its environment.

The control architecture is powered by an ESP32 dual-core microcontroller running custom firmware, which interfaces with a dedicated Python API over Wi-Fi or Ethernet. Supporting hardware includes a custom PCB for power distribution and sensor integration. The final prototype demonstrates a modular approach to robotics, providing a scalable platform for precise manipulation and future iterative upgrades.

\section*{Keywords:}
% TODO: add keywords that best describe the thesis topic
% \noindent 
\section*{Field of science and technology in accordance with OECD requirements:}
% TODO: check the list of fields of science and technology in accordance with OECD requirements and select the appropriate one for the thesis.
% \noindent engineering and technology; electrical, electronic and information engineering; robotics and automation; telecommunications. 