%% ============================================================
%% Chapter 4 — Summary and Conclusions
%% ============================================================
\chapter{Summary}\label{chapter:4_Summary}
This chapter should provide a brief summary of the entire thesis, highlighting the most important achievements, results, and conclusions from the research or project implementation. The purpose of this part is to present the extent to which the assumed objectives have been achieved and what practical or scientific significance the obtained results have.

The summary should also include a reflection on the difficulties and limitations encountered that may have affected the course of work or the results. It is also advisable to formulate suggestions regarding possible directions for further research, project development, or improvement.

\section{Conclusions}
The conclusions constitute a concise compilation of the key observations and results obtained in the thesis. They should be presented as an organised list, with an emphasis on the practical significance of the results and their consistency with the previously stated objectives and hypotheses.

\section{The way forward}
\noindent This subsection should indicate possible directions for expanding, optimising, or applying the developed solution. It may also describe:
\begin{itemize}
    \item potential functional or technical improvements
    \item the possibility of integration with other systems
    \item application of the results in engineering, scientific, or industrial practice
    \item further studies or tests enabling verification of the effectiveness of the proposed approach
\end{itemize}

\noindent To conclude, this chapter should constitute the final, logical stage of the thesis, presenting its contribution and indicating how it can be further developed or used in the future.
